Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-10 main.tex
comments

For a formula $A$, we can define its
associated fograph $\graphof(A)$ inductively by: 
\begin{equation*}
  \begin{array}{l}
    \graphof{\alpha} = \cdot \alpha (\text{single-vertex graph whose vertex is 
    labelled by } \alpha); \\[.5ex]
    \graphof{A \cor B} = \graphof{A} + \graphof{B};
    \graphof{A \cand B} = \graphof{A} \times \graphof{B}; \\[.5ex]
    \graphof{\forall x . A} = \cdot x + \graphof{A};
    \graphof{\exists x . A} = \cdot x \times \graphof{A}.
  \end{array}
\end{equation*}
\todo{make look nice, use array} \juihsuan{done}

@@

\todo{define matching} \juihsuan{done in the cograph part}

>>>>

For a formula $A$, we can define its
associated fograph $\graphof(A)$ inductively by: 
\begin{equation*}
  \begin{array}{l}
    \graphof{\alpha} = \cdot \alpha (\text{single-vertex graph whose vertex is 
    labelled by } \alpha); \\[.5ex]
    \graphof{A \cor B} = \graphof{A} + \graphof{B};
    \graphof{A \cand B} = \graphof{A} \times \graphof{B}; \\[.5ex]
    \graphof{\forall x . A} = \cdot x + \graphof{A};
    \graphof{\exists x . A} = \cdot x \times \graphof{A}.
  \end{array}
\end{equation*}
\todo{make look nice, use array} \juihsuan{done}\lutz{use the single macro (see above), so that we can change the notation later if we need to (and make the array with two columns)}

@@

\todo{define matching} \juihsuan{done in the cograph part}\lutz{no, it should be here}
